gij bent 2

### 2024-12-09 paper/paper.qmd
Fix West Flanders correction

[^anomaly]: The results for the West-Flemish dialect area need to be interpreted in conjunction with the "distance from northern Antwerp" parameter. The regression analysis assumes a zero distance from Antwerp from the intercept, but this does not make sense for dialect areas other than Brabant. Therefore, if we apply the extra corrections expressed in "distance from northern Antwerp", we get the expected negative correction towards the conservative form (`r 121 * -0.017`). Still, the *gij* pronoun is quite rare in this area, so the West-Flemish results should be treated with caution.

>>>>

[^anomaly]: The results for the West-Flemish dialect area need to be interpreted in conjunction with the "distance from northern Antwerp" parameter. The regression analysis assumes a zero distance from Antwerp from the intercept, but this does not make sense for dialect areas other than Brabant. Therefore, if we apply the extra corrections expressed in "distance from northern Antwerp", we get the expected negative correction towards the conservative form (`r (121 * coefficients_full %>% filter(feature == "_distance_from_antwerp") %>% .$coefficient) %>% formatd(3)`). Still, the *gij* pronoun is quite rare in this area, so the West-Flemish results should be treated with caution.
